\systemnamenospace: Head Orientation Based Selection\\in Physical Spaces

### 2014-06-28 doc/sui14/applications.tex
grammer fixes

% \bjoern{1 is problematic - because it sounds like that the head worn device is in the end not worth it and you should just use your phone, even if it takes longer. I'm not sure we can confidently say something about museums or body shops - this sounds speculative. Needs section needs to be rephrased., e.g. as in: Our solution succeeds at X because of Y. This suggests that future applications in domains like Z could be especially promising.}
\changes{While our system enabled users to select and control the example devices successfully, work remains in devising appropriate interfaces for complex devices. Users rated ease of use higher for the lamp and fan which had simple, discrete on/off actions, and lower for the TV control, which had more options. Multiple participants remarked that the difficulty was based on the affordances of Glass: \studyquote{Most of the difficulty I had with Glass came from having to navigate the interface on the tiny screen with the touch pad}. 
We leave addressing this fundamental usability challenge of wearable devices with near-eye displays to future work.}
%\changes{Though our solution successfully solves the problem of {\em target selection}, we have not fully addressed the issue of controlling smart devices. One user reported that \studyquote{for more complex appliances (TV), interaction was more difficult}. A separate work on interaction techniques for head-worn computing devices is needed to address these issues, while we keep our focus on target selection.} \ben{ Suggest to remove this one: When the device is more complicated, it is possible that a better solution may be a hybrid -- to select the appliance with HOBS and control it with a phone.} \claire{ Is it possible to say that the number of complicated devices that you want to remote control is limited almost exclusively to the tv? I can't think of too many of these devices and our system works very well with more simple devices, which seem to be more common.} \sean{ I wouldn't state that. We could be challenged if the reviewers bring up smart fridge, microwave, etc.}

>>>>

% \bjoern{1 is problematic - because it sounds like that the head worn device is in the end not worth it and you should just use your phone, even if it takes longer. I'm not sure we can confidently say something about museums or body shops - this sounds speculative. Needs section needs to be rephrased., e.g. as in: Our solution succeeds at X because of Y. This suggests that future applications in domains like Z could be especially promising.}
\changes{While our system enables users to select and control the example devices successfully, work remains in devising appropriate interfaces for complex devices. Users rated ease of use higher for the lamp and fan which had simple, discrete on/off actions, and lower for the TV control, which had more options. Multiple participants remarked that the difficulty was based on the affordances of Glass: \studyquote{most of the difficulty I had with Glass came from having to navigate the interface on the tiny screen with the touch pad}. 
We leave addressing this fundamental usability challenge of wearable devices with near-eye displays to future work.}
%\changes{Though our solution successfully solves the problem of {\em target selection}, we have not fully addressed the issue of controlling smart devices. One user reported that \studyquote{for more complex appliances (TV), interaction was more difficult}. A separate work on interaction techniques for head-worn computing devices is needed to address these issues, while we keep our focus on target selection.} \ben{ Suggest to remove this one: When the device is more complicated, it is possible that a better solution may be a hybrid -- to select the appliance with HOBS and control it with a phone.} \claire{ Is it possible to say that the number of complicated devices that you want to remote control is limited almost exclusively to the tv? I can't think of too many of these devices and our system works very well with more simple devices, which seem to be more common.} \sean{ I wouldn't state that. We could be challenged if the reviewers bring up smart fridge, microwave, etc.}

### 2014-06-28 doc/sui14/conclusion.tex
grammer fixes

In this paper, by presenting our iterative design process in head-orientation based targeting, we have learned that IR alone can help reduce the overall acquisition time by reducing the chances when we need to perform refinement. With IR intensity added, the targeting can work better in a relative dense environment. However, a more natural approach is to combine IR with head motion. Through our preliminary user studies, we learned that this is a more intuitative way of performing refinement in comparison to the menu-based selections. We leave a more comprehensive technical solution of using motion sensors and its evaluation as the future work.

>>>>

In this paper, by presenting our iterative design process in head-orientation based targeting, we have learned that IR alone can help reduce the overall acquisition time by reducing the chances when we need to perform refinement. With IR intensity added, the targeting can work better in a relative dense environment. However, a more natural approach is to combine IR with head motion. Through our preliminary user studies, we learned that this is a more intuitive way of performing refinement in comparison to the menu-based selections. We leave a more comprehensive technical solution of using motion sensors and its evaluation as the future work.

### 2014-06-28 doc/sui14/discussion.tex
grammer fixes

We also acknowledge several limitations of our study design: we have not yet systematically studied target density variation, our study was performed in a lab environment, and only measured first use. Future work should study how the technique applies in realistic settings over longer periods of time.

>>>>

We also acknowledge several limitations of our study design: we have not yet systematically studied target density variation; our study was performed in a lab environment; and only measured first use. Future work should study how the technique applies in realistic settings over longer periods of time.

### 2014-06-28 doc/sui14/interaction.tex
grammer fixes

\changes{IR signals are used for intial line-of-sight targeting; subsequently, we use bi-directions wireless communication to send information such as target IDs and signal strength from targets to back to Glass. We have chosen the commercial off-the-shelf ZigBee implementation (XBee based on 802.15.4 radio) for this purpose (see Figure~\ref{fig:architecture}). This architecture was mostly chosen for reasons of expediency and we do not claim optimality for prototyping decisions. Future head-mounted devices could clearly integrate IR emitters; other wireless techniques (WiFi, Bluetooth) can also be used.}

@@

{\bf Refine:} When disambiguation is needed, the user must make an explicit selection among the targets within their view range. We have designed multiple refinement mechanisms -- all of which enable the user to select one from a subset of targets. The user confirms a current selection with a tap. Since the purpose of this stage is to disambiguate among potential targets, we will also use {\em disambiguation} to refer to this stage. Finally, a tap confirms a decision.

>>>>

\changes{IR signals are used for initial line-of-sight targeting; subsequently, we use bi-directions wireless communication to send information such as target IDs and signal strength from targets to back to Glass. We have chosen the commercial off-the-shelf ZigBee implementation (XBee based on 802.15.4 radio) for this purpose (see Figure~\ref{fig:architecture}). This architecture was mostly chosen for reasons of expediency and we do not claim optimality for prototyping decisions. Future head-mounted devices could clearly integrate IR emitters; other wireless techniques (WiFi, Bluetooth) can also be used.}

@@

{\bf Refine:} When disambiguation is needed, the user must make an explicit selection among the targets within their view range. We have designed multiple refinement mechanisms -- all of which enable the user to select one from a subset of targets. The user confirms the current selection with a tap. Since the purpose of this stage is to disambiguate among potential targets, we will also use {\em disambiguation} to refer to this stage. Finally, a tap confirms a decision.

### 2014-06-28 doc/sui14/iteration2.tex
use 0.95 for all figures
grammer fixes

\begin{figure}[t]
\centering
\includegraphics[width=1\columnwidth]{figures/IRIntensityDistribution.pdf}
\caption{Empirical measurement of IR intensity at different position. We measure the intensity at a plane every meter away from the IR emitter. On that plane, we obtain a sample every 5 centimeters. The size and color brightness in this graph represents the intensity readings.}
\label{fig:measurement}
\end{figure}

@@

\subsection{Method}
To quantify the improvement in this design we performed a second study to compare the {\em Naive IR} and {\em Intensity IR} approaches. Because we were interested in discovering performance differences in denser environment, we reposition the 10 nodes and set them up in a smaller area (see Figure~\ref{fig:study-layout2}). We recruited 10 participants for this study. Each  user performed 30 target acquisition tasks for each approach. As in our first within-subject study, half of them perform {\em Naive IR} first and the other half {\em Intensity IR} first.

\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{figures/study-layout2.pdf}
\caption{The environment setup for our second study. In comparison to our first study, we have deliberately increased the target density.}
\label{fig:study-layout2}
\end{figure}

@@

From Figure~\ref{fig:study2}, we can see that the overall target acquisition time has decreased from 4.31 seconds for {\em Naive IR} to 3.64 second for {\em Intensity IR}. This difference is also significant ($t(555)=3.2945$, $p=0.001$.)

@@

\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{figures/result_study2.pdf}
\caption{Boxplot and CDF of the target acquisition time in {\em Naive IR} and {\em Intensity IR} conditions.}
\label{fig:study2}
\end{figure}

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=0.95\columnwidth]{figures/IRIntensityDistribution.pdf}
\caption{Empirical measurement of IR intensity at different positions. We measure the intensity at a plane every meter away from the IR emitter. On that plane, we obtain a sample every 5 centimeters. The size and color brightness in this graph represents the intensity readings.}
\label{fig:measurement}
\end{figure}

@@

\subsection{Method}
To quantify the improvement in this design we performed a second study to compare the {\em Naive IR} and {\em Intensity IR} approaches. Because we were interested in discovering performance differences in denser environment, we re-positioned the 10 nodes and set them up in a smaller area (see Figure~\ref{fig:study-layout2}). We recruited 10 participants for this study. Each  user performed 30 target acquisition tasks for each approach. As in our first within-subject study, half of them perform {\em Naive IR} first and the other half {\em Intensity IR} first.

\begin{figure}[t]
\centering
\includegraphics[width=0.95\columnwidth]{figures/study-layout2.pdf}
\caption{The environment setup for our second study. In comparison to our first study, we have deliberately increased the target density.}
\label{fig:study-layout2}
\end{figure}

@@

From Figure~\ref{fig:study2}, we can see that the overall target acquisition time has decreased from 4.31 seconds for {\em Naive IR} to 3.64 second for {\em Intensity IR}. This difference is also significant ($t(555)=3.2945$, $p=0.001$).

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.95\columnwidth]{figures/result_study2.pdf}
\caption{Boxplot and CDF of the target acquisition time in {\em Naive IR} and {\em Intensity IR} conditions.}
\label{fig:study2}
\end{figure}
